Comparison with Christensen paper

### 2018-12-20 paper-comparison/compare-christensen.Rmd
Set up to run paper cpt on LDATS lda

ldats_dat <- as.matrix(ch_dat)
ldats_dat <- apply(ldats_dat, c(1,2), FUN = as.integer)
rodents$document_term_table <- ldats_dat
rm(ldats_dat)
rm(ldats_dates)
rm(ch_dates)
rm(ch_dat)
```

@@

```{r LDATS LDA + LDATS cpt}
# Run changepoint

@@

save(ldats_ldats_selected, file = 'model-stash/ldats_ldats_selected.Rds')

@@

>>>>

ldats_dat <- as.matrix(ch_dat)
ldats_dat <- apply(ldats_dat, c(1,2), FUN = as.integer)
rodents$document_term_table <- ldats_dat
rm(ldats_dat)
rm(ldats_dates)
rm(ch_dat)
```

@@

```{r LDATS LDA + LDATS cpt, eval = F}
# Run changepoint

@@

save(ldats_ldats_selected, file = '/Users/renatadiaz/Documents/model-stash/ldats_ldats_selected.Rds')

@@

```{r, eval = F}
rm(ldats_ldats)
rm(ldats_ldats_selected)
```

```{r paper cpt on LDATS LDA}
source('christensen-ecology-files/changepointmodel.r')
# set up parameters for model
year_continuous = 1970 + as.integer(julian(ch_dates)) / 365.25
x = data.frame(
  year_continuous = year_continuous,
  sin_year = sin(year_continuous * 2 * pi),
  cos_year = cos(year_continuous * 2 * pi)
)

```{r, eval = F}
# run models with 1, 2, 3, 4, 5 changepoints
cp_results_rodent = changepoint_model(ldats_lda_selected[[1]], x, 1, weights = rep(1,length(year_continuous)))
cp_results_rodent2 = changepoint_model(ldats_lda_selected[[1]], x, 2, weights = rep(1,length(year_continuous)))
cp_results_rodent3 = changepoint_model(ldats_lda_selected[[1]], x, 3, weights = rep(1,length(year_continuous)))
cp_results_rodent4 = changepoint_model(ldats_lda_selected[[1]], x, 4, weights = rep(1,length(year_continuous)))
cp_results_rodent5 = changepoint_model(ldats_lda_selected[[1]], x, 5, weights = rep(1,length(year_continuous)))
cp_results_rodent6 = changepoint_model(ldats_lda_selected[[1]], x, 6, weights = rep(1,length(year_continuous)))

paper_ldats <- list(cp_results_rodent, cp_results_rodent2,
                    cp_results_rodent3, cp_results_rodent4,
                    cp_results_rodent5, cp_results_rodent6)

rm(list = c('cp_results_rodent', 'cp_results_rodent2',
                    'cp_results_rodent3', 'cp_results_rodent4',
                    'cp_results_rodent5', 'cp_results_rodent6'))

save(paper_ldats, file = '/Users/renatadiaz/Documents/model-stash/paper_cpt_ldats_lda.Rds')
